---
title: "Urban soils analysis"
author: "Gordon Fitch"
date: "`r Sys.Date()`"
output: html_document
---

```{r}
# R itself for this project is version 4.5.2 as of Oct 16th 2025
library(corrplot) #V1.1.6
library(dplyr) #V1.1.4
library(factoextra) #v2.0.0
library(FSA) #V0.10.1
library(ggplot2) #V4.0.0
library(ggpubr) #V0.6.1
# I am pretty sure this package is no longer being used but keeping it here
library(ggsignif) #V0.6.4
library(glmmTMB) #V1.1.13
library(lavaan) #V0.6-20
library(piecewiseSEM) #V2.3.1
library(readr) #V2.1.5
# Apparently this is faster than read.csv? Will try it, hopefully nothing breaks
# Also I am pretty sure this package is no longer being used but keeping it here
library(Rmoji) #V0.1.0 #priorities
library(rstatix) #V0.7.2
# Again this package is no longer being used~ but keeping it here
library(scales) #V1.4.0
library(semPlot) #V1.1.7
library(tidyverse) #V2.0.0
library(vegan) #V2.7-1
```

### Read in data
```{r}
soils <- read_csv("~/Documents/repos/turbpe/spreadsheets/soil.csv")
bee_captures <- read_csv("~/Documents/repos/turbpe/spreadsheets/bee_captures.csv")
```

### Run PCA and basic plot
```{r}
pca.soil <- prcomp(soils[,c(5:38)], center = T, scale = T)
biplot(pca.soil)
```

### Plot with site type, area, and roadside ellipses
```{r}
fviz_ellipses(pca.soil, 
              as.factor(soils$Type),
              graph.type = "ggplot", 
              ggtheme = theme_minimal(),
              pointsize=2, 
              geom="point", 
              ellipse.level = 0.95, ellipse.type = c("confidence"))

fviz_ellipses(pca.soil, 
              as.factor(soils$Area),
              graph.type = "ggplot", 
              ggtheme = theme_minimal(),
              pointsize=2, 
              geom="point", 
              ellipse.level = 0.95, ellipse.type = c("confidence"))

fviz_ellipses(pca.soil, 
              as.factor(soils$Roadside),
              graph.type = "ggplot", 
              ggtheme = theme_minimal(),
              pointsize=2, 
              geom="point", 
              ellipse.level = 0.95, ellipse.type = c("confidence"))
```

### Plots showing contribution of elements to PC1 & PC2
```{r}
fviz_contrib(pca.soil, choice="var", axes = 1,
              fill = "lightgray", color = "black") +
     theme_minimal() +
     theme(axis.text.x = element_text(angle=45))

fviz_contrib(pca.soil, choice="var", axes = 2,
              fill = "lightgray", color = "black") +
     theme_minimal() +
     theme(axis.text.x = element_text(angle=45))
```

### Extract PC1 from plot for use as predictor in models
```{r}
pca.results <- as.data.frame(pca.soil$x)
pca.site <- cbind(soils[,c(1:4)], pca.results)
```

### NMDS (another kind of ordination)
```{r}
soils.matrix <- soils[,c(5:38)]
NMDS <- metaMDS(soils.matrix,k=2)
NMDS #stress = 0.18

data.scores <- as.data.frame(scores(NMDS)$sites)  #Using the scores function from vegan to extract the site scores and convert to a data.frame
data.scores$sample <- soils$Client.Sample.ID  # create a column of site names, from the rownames of data.scores
data.scores$area <- soils$Area
data.scores$type <- soils$Type
data.scores$road <- soils$Roadside
element.scores <- as.data.frame(scores(NMDS, "species"))  #Using the scores function from vegan to extract the species scores and convert to a data.frame
element.scores$elements <- rownames(element.scores)

#create hulls for type
type.N <- data.scores[data.scores$type == "Negative control", ][chull(data.scores[data.scores$type == 
    "Negative control", c("NMDS1", "NMDS2")]), ]  # hull values for negative controls
type.P <- data.scores[data.scores$type == "Positive control", ][chull(data.scores[data.scores$type == 
    "Positive control", c("NMDS1", "NMDS2")]), ]  # hull values for positive controls
type.T <- data.scores[data.scores$type == "Treatment", ][chull(data.scores[data.scores$type == 
    "Treatment", c("NMDS1", "NMDS2")]), ]  # hull values for treatments
hull.data <- rbind(type.N, type.P, type.T)

#plot NMDS with location hulls
ggplot() + 
  geom_polygon(data=hull.data,aes(x=NMDS1,y=NMDS2,fill=type, group=type),alpha=0.30) + # add the convex hulls
  geom_text(data=element.scores,aes(x=NMDS1,y=NMDS2,label=elements),alpha=0.5) +  # add the element labels
  geom_point(data=data.scores,aes(x=NMDS1,y=NMDS2,shape=type,colour=type),size=4) + # add the point markers
  coord_equal() +
  theme_bw() + 
  theme(axis.text.x = element_blank(),  # remove x-axis text
        axis.text.y = element_blank(), # remove y-axis text
        axis.ticks = element_blank(),  # remove axis ticks
        axis.title.x = element_text(size=18), # remove x-axis labels
        axis.title.y = element_text(size=18), # remove y-axis labels
        panel.background = element_blank(), 
        panel.grid.major = element_blank(),  #remove major-grid labels
        panel.grid.minor = element_blank(),  #remove minor-grid labels
        plot.background = element_blank())

#create hulls for roadside or not
road.Y <- data.scores[data.scores$road == "Y", ][chull(data.scores[data.scores$road == 
    "Y", c("NMDS1", "NMDS2")]), ]  # hull values for roadside sites
road.N <- data.scores[data.scores$road == "N", ][chull(data.scores[data.scores$road == 
    "N", c("NMDS1", "NMDS2")]), ]  # hull values for positive controls
hull.data.road <- rbind(road.Y, road.N)

#plot NMDS with location hulls
ggplot() + 
  geom_polygon(data=hull.data.road, aes(x=NMDS1,y=NMDS2,fill=road, group=road),alpha=0.30) + # add the convex hulls
  geom_text(data=element.scores,aes(x=NMDS1,y=NMDS2,label=elements),alpha=0.5) +  # add the element labels
  geom_point(data=data.scores,aes(x=NMDS1,y=NMDS2,shape=road,colour=road),size=4) + # add the point markers
  coord_equal() +
  theme_bw() + 
  theme(axis.text.x = element_blank(),  # remove x-axis text
        axis.text.y = element_blank(), # remove y-axis text
        axis.ticks = element_blank(),  # remove axis ticks
        axis.title.x = element_text(size=18), # remove x-axis labels
        axis.title.y = element_text(size=18), # remove y-axis labels
        panel.background = element_blank(), 
        panel.grid.major = element_blank(),  #remove major-grid labels
        panel.grid.minor = element_blank(),  #remove minor-grid labels
        plot.background = element_blank())
```

Follow-up here, I wanna compare soil NMDS data per site type to average bee
captures per site each sampling sorted by site type. Past this I think it's
redundant to analyze for now since it'll just give more lack of associations
right?
```{r}
# Process Bee Captures in memory
# Counting bees per Site per Date, then average those daily counts per Site
bee_abundance_stats <- bee_captures %>%
  # Identify Type based on the first letter of the Site column
  mutate(type_from_bee = case_when(
    grepl("^P", Site) ~ "Positive control",
    grepl("^N", Site) ~ "Negative control",
    grepl("^T", Site) ~ "Treatment",
    TRUE ~ "Other"
  )) %>%
  # Step A: Get total bees caught per unique day at each site
  group_by(Site, Date, type_from_bee) %>%
  summarise(daily_total = n(), .groups = "drop") %>%
  # Step B: Get the average of those daily totals for each site
  group_by(Site) %>%
  summarise(avg_bee_abundance = mean(daily_total), .groups = "drop")

# Fix Site name mapping in NMDS scores
# Note the backticks used for the column name with spaces
data.scores$sample <- soils$`Client Sample ID`

# Join the bee stats to NMDS coordinates
# This adds 'avg_bee_abundance' as a column to your data.scores
data.scores <- data.scores %>%
  left_join(bee_abundance_stats, by = c("sample" = "Site"))

# Plot NMDS with point size reflecting Bee Abundance
ggplot() + 
  # Add the hulls from your original code
  geom_polygon(data=hull.data, aes(x=NMDS1, y=NMDS2, fill=type, group=type), alpha=0.2) +
  # Add element (species) labels
  geom_text(data=element.scores, aes(x=NMDS1, y=NMDS2, label=elements), alpha=0.4, size=3) +
  # Add points where SIZE is determined by bee abundance
  geom_point(data=data.scores, aes(x=NMDS1, y=NMDS2, shape=type, colour=type, size=avg_bee_abundance)) +
  scale_size_continuous(name = "Avg Daily Bees") +
  coord_equal() +
  theme_bw() + 
  labs(title = "Soil NMDS Ordination",
       subtitle = "Point size represents average bees caught per sampling day") +
  theme(panel.grid = element_blank())

# Quick Correlation Test
# Does the soil gradient (NMDS1) correlate with bee abundance?
cor.test(data.scores$NMDS1, data.scores$avg_bee_abundance, method = "spearman")
```
Gawdamn this NMDS figure is useless, well at least it gives the obvious
association I was after