Working directory info: IMPORTANT NOTE, keep this directory listing identical
to minimize wd errors between devices working on the same repository
  Yes that means please create a folder called "repos"
```{r}
setwd("~/Documents/repos/turbpe")
```

Packages list, plus Audrey's versions of each package
  I didn't make it mandatory to download a specific version of each package as I
  don't want anyone to make redundant downloads, just commented what I'm using
  FYI Andrew we should pretty much always be using the same versions of packages
  since we're both on macbook M4 silicone chips, so this should never be
  something to worry about for you
```{r}
library(corrplot) #V1.1.6
library(dplyr) #V1.1.4
library(ggplot2) #V4.0.0
library(lavaan) #V0.6-20
library(piecewiseSEM) #V2.3.1
library(readr) #V2.1.5
#apparently this is faster than read.csv? Will try it, hopefully nothing breaks
library(scales) #V1.4.0
library(semPlot) #1.1.7
library(tidyverse) #V2.0.0
library(vegan) #V2.7-1

```


Most frequent bees across sites
```{r}

````
