Sorry Gordon I got tired of everything being in one file, it's just not for me
Anyways I'll keep the rarefaction and like in here for now, may be changed in
the future, I would like to have a lean comprehensive RMD document for the
research related to this thesis (and definitely ones for separate publications),
but that will be a final steps/touch ups thing. My brain works better with
separate files in a directory I think. I mean rmd files are basically 
collections of executable R files in one page, to me it's pointlessly
ungraceful if I also don't separate like this

Anyways first packages stuff, will keep the same package list across all files
```{r}
# R itself for this project is version 4.5.1 as of Oct 16th 2025
library(corrplot) #V1.1.6
library(dplyr) #V1.1.4
library(ggplot2) #V4.0.0
library(ggpubr) #V0.6.1
# I am pretty sure this package is no longer being used but keeping it here
library(ggsignif) #V0.6.4
library(glmmTMB) #V1.1.13
library(lavaan) #V0.6-20
library(piecewiseSEM) #V2.3.1
library(readr) #V2.1.5
# Apparently this is faster than read.csv? Will try it, hopefully nothing breaks
# Also I am pretty sure this package is no longer being used but keeping it here
library(rstatix) #V0.7.2
# Again this package is no longer being used~ but keeping it here
library(scales) #V1.4.0
library(semPlot) #V1.1.7
library(tidyverse) #V2.0.0
library(vegan) #V2.7-1
```

BUT what I will do differently here, is work on datasets one at a time and bring
them up when necessarily/applicable. I am not sure if this is the right way to
go about things, but I will do so for now, maybe this approach will be good for
me who knows?
I also realize that "bees" is a different title to bee_captures(_8th) in the
previous files, but this should have been how I went about it anyways, or rather
the bee_captures_8th was always a placeholder
```{r}
bees <- read_csv("~/Documents/repos/turbpe/spreadsheets/bee_captures.csv")
```

