Sorry Gordon I got tired of everything being in one file, it's just not for me
Anyways I'll keep the rarefaction and like in here for now, may be changed in
the future, I would like to have a lean comprehensive RMD document for the
research related to this thesis (and definitely ones for separate publications),
but that will be a final steps/touch ups thing. My brain works better with
separate files in a directory I think. I mean rmd files are basically 
collections of executable R files in one page, to me it's pointlessly
ungraceful if I also don't separate like this

Anyways first packages stuff, will keep the same package list across all files
```{r}
# R itself for this project is version 4.5.1 as of Oct 16th 2025
library(corrplot) #V1.1.6
library(dplyr) #V1.1.4
library(FSA) #V0.10.1
library(ggplot2) #V4.0.0
library(ggpubr) #V0.6.1
# I am pretty sure this package is no longer being used but keeping it here
library(ggsignif) #V0.6.4
library(glmmTMB) #V1.1.13
library(lavaan) #V0.6-20
library(piecewiseSEM) #V2.3.1
library(readr) #V2.1.5
# Apparently this is faster than read.csv? Will try it, hopefully nothing breaks
# Also I am pretty sure this package is no longer being used but keeping it here
library(Rmoji) #V0.1.0 #priorities
library(rstatix) #V0.7.2
# Again this package is no longer being used~ but keeping it here
library(scales) #V1.4.0
library(semPlot) #V1.1.7
library(tidyverse) #V2.0.0
library(vegan) #V2.7-1
```

BUT what I will do differently here, is work on datasets one at a time and bring
them up when necessarily/applicable. I am not sure if this is the right way to
go about things, but I will do so for now, maybe this approach will be good for
me who knows?
```{r}
bee_captures <- read_csv("~/Documents/repos/turbpe/spreadsheets/bee_captures.csv")
```

Okay this is to make the base
```{r}
# Clean the data to create desired categories
bee_captures <- read.csv("~/Documents/repos/turbpe/spreadsheets/bee_captures.csv")

bee_captures_clean <- bee_captures %>%
  mutate(
    # Combine Family and Genus for one collective placeholder diversity metric
    # Since yknow sometimes there are species names that are shared between
    # different genuses, then I realized that I'm an idiot because I'm only
    # working on genus right now, but hey yknow what it's fine, later this can
    # be swapped for Genus and species instead and all will be good in the world
    Taxa = paste(Family, Genus, sep = "_"),
    
    # Make an actual category from the 2nd character of Site, something
    # something dataframes are good for this sort of stuff?
    Category_Code = substr(Site, 2, 2),
    Category = case_when(
      Category_Code == "P" ~ "Wildflower park",
      Category_Code == "T" ~ "Wildflower roadside",
      Category_Code == "N" ~ "Mowed roadside",
      TRUE ~ "Unknown"
    ),
    
    # Define unique Sampling Event
    Sampling_Event = paste(Site, Date, sep = "_")
  )

# Calculate observed richness per sampling event
event_summary <- bee_captures_clean %>%
  group_by(Category, Sampling_Event) %>%
  summarise(
    Observed_Richness = n_distinct(Taxa),
    Total_Individuals = n(),
    .groups = "drop"
  )

# Making observed diversity boxplot figure
ggplot(event_summary, aes(x = Category, y = Observed_Richness, fill = Category)) +
  geom_boxplot(alpha = 0.7) +
  geom_jitter(width = 0.2, alpha = 0.5) + # Optional: shows individual events
  labs(title = "Observed Bee Diversity (Genus Level) per Sampling Event",
       y = "Number of Unique Genera", 
       x = "Treatment Category") +
  theme_minimal()
```

Now to apply rarefaction
```{r}
# Define a target number of individuals (n). 
# Samples with fewer than 'n' individuals will be excluded from the rarefied plot.
n_target <- 5 

rarefied_results <- bee_captures_clean %>%
  group_by(Category, Sampling_Event) %>%
  summarise(
    # what is this why is this needed I don't get it aaaa
    Rarefied_Richness = {
      counts <- table(Taxa)
      if(sum(counts) >= n_target) rarefy(counts, n_target) else NA
    },
    .groups = "drop"
  ) %>%
  filter(!is.na(Rarefied_Richness))

# Making rarefied diversity boxplot figure
ggplot(rarefied_results, aes(x = Category, y = Rarefied_Richness, fill = Category)) +
  geom_boxplot(alpha = 0.7) +
  geom_jitter(width = 0.2, alpha = 0.5) +
  labs(title = paste("Rarefied Bee Diversity (at n =", n_target, "individuals)"),
       subtitle = "Standardized diversity accounting for sampling effort",
       y = "Expected Genus Richness", 
       x = "Site type") +
  theme_minimal()
```

RAAAAAAA look the no statistical significance 🔥🔥🔥
Oh right what was I saying, right this is the Kruskal-Wallis test, this is good
for rarefied data and (later) alpha/beta diversity analyses I think?
```{r}
obs_test <- kruskal.test(Observed_Richness ~ Category, data = event_summary)
print(obs_test)

# If significant (p < 0.05), run a Post-hoc test to see which groups differ
if(obs_test$p.value < 0.05) {
  library(FSA)
  dunnTest(Observed_Richness ~ Category, data = event_summary, method="bh")
}
```

Wilcoxon/Mann-Whitney test
```{r}
# Filter for just the two main groups cuz negative is so obviously different and
# messes with stats
rar_subset <- rarefied_results %>% filter(Category %in% c("Positive", "Treatment"))

wilcox_test <- wilcox.test(Rarefied_Richness ~ Category, data = rar_subset)
print(wilcox_test)
```

Time to apply the same rarefaction to plants? I do have these at species level
```{r}
flowers <- read_csv("~/Documents/repos/turbpe/spreadsheets/flowers.csv")
```

